Twists of supersymmetric gauge theories

### 2019-07-21 paper.tex
small changes

A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$, see Definition \ref{dfn: fnl} in the appendix. 
The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
\[
\left(\cO(\cE), Q + \{I,-\}\right) .
\]
In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
We will refer to this as the {\bf classical BV complex} of the theory.

@@

Let $(E, Q, \omega, I)$ be a classical field theory and suppose $\psi_0 \in \sE$ is a fixed solution to the equations of motion. 
Then, we recall the formalism of \cite{CG1,CG2} which extracts a factorization algebra on spacetime that should be thought of as  functions on the formal neighborhood of the derived critical locus of the action $S$ near $\psi_0$.

@@

Notice that the BV complex we defined in the previous section is simply the global sections of the factorization algebra along $M$.

@@

If $M$ is a smooth manifold, its {\em de Rham stack}, as a dg ringed space, is 
\[
M_{\rm dR} = \left(M , (\Omega^*_M, \d_{\rm dR})\right) .
\]

If $X$ is a complex manifold, there are two naturally associated dg ringed spaces that will be important for us. 
The first is the $\dbar$-{\em stack}, defined by
\[
X_{\dbar} = \left(M , (\Omega^{0,*}_X, \dbar) \right) .
\]
The next is the {\em Dolbeault stack}, defined by
\[
X_{\rm Dol} = \left(M, (\Omega^{*,*}_X, \dbar)\right) .
\] 
Note that as sheaves of dg modules, there is a quasi-isomorphism $(\Omega^{p,*}_M, \dbar) = \Omega^{p, hol}_M$.
Thus, one can think of the underlying ring of the Dolbeault stack as functions on the shifted holomorphic tangent bundle $T^{1,0} [1] M$ of $M$.

@@

\begin{dfn}
Let $X,Y$ be complex manifolds and $M$ a smooth manifold.
Let $\fg$ be an $L_\infty$ algebra which is finite dimensional in each cohomological degree. 
The {\bf mixed holomorphic-Dolbeault-topological BRST theory} \brian{blah, terrible name} on $X \times Y \times M$ is the local $L_\infty$ algebra defined by
\[
\cF[-1] = \Omega^{0,*}_X \Hat{\otimes} \Omega^{*,*}_Y \Hat{\otimes} \Omega^*_M \otimes \fg .
\] 
The $L_\infty$ structure is the one induced from $\fg$ together with the dg commutative products on differential forms. 
This is a classical BRST theory by choosing $Q_{BRST} = 0, I_{BRST} = 0$. 
In other words, $\cF$ is defined by the mapping stack
\[
{\rm Map} (X_{\dbar} \times Y_{\rm Dol} \times M_{\rm dR}, B \fg) .
\]

The {\bf mixed holomorphic-Dolbeault-topological BF theory} is the BV theory given by the $(-1)$-shifted cotangent bundle to $\cF$.

@@

Fix a Calabi-Yau manifold $X$ of complex dimension $n$, and let $\fg$ be a $\ZZ/2$-graded Lie algebra with a non-degenerate graded symmetric pairing of parity opposite to $n$. 
In particular, for odd $n$ we can take an ordinary complex semi-simple Lie algebra $\fg$ with its Killing form. 
When $n$ is even must work with a graded Lie algebra with an odd pairing.
In any case, we denote the pairing by $\<-,-\>$.

\begin{dfn}
Let $X, \fg$ be as above.
{\bf Holomorphic Chern-Simons theory} on $X$ with values in $\fg$ is the $\ZZ/2$-graded classical field theory $(E_\hCS, Q_\hCS, \omega_\hCS, I_\hCS)$, where the space of fields is given by the Dolbeault complex with coefficients in $\gg$
\[
\cE_\hCS = \Omega^{0,\bullet}(X;\gg)[1],
\]
$Q_{\hCS} = \dbar$ is the Dolbeault differential, $\omega_\hCS$ is the density-valued pairing
\[
\omega_{\hCS} (\alpha,\beta) = \<\alpha \wedge \beta\> \wedge \Omega_X,
\]
where $\Omega_X$ is the Calabi-Yau structure on $X$, and $I_\hCS$ is the cubic interactional functional
\[
I_{\hCS}(\alpha) = \frac 16 \<\alpha \wedge [\alpha, \alpha]\> \wedge \Omega_X .
\]
\end{dfn}

\begin{eg} 
Let $X$ be a Calabi-Yau $2$-fold, like $\CC^2$, and let $\fh$ be an ordinary Lie algebra equipped with an invariant non-degenerate symmetric pairing $\<-,-\>_\fh$. 
Define the $\ZZ/2$-graded Lie algebra
\[
\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3] 
\]
where $\epsilon_i$ are odd formal variables.

@@

With this data, holomorphic Chern-Simons on the $2$-fold $X$ with values in $\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3]$ is defined. 
\brian{check this} In fact, in this example, there is a natural lift to a $\ZZ$-graded theory whereby the coordinates $\epsilon_i$ are given cohomological degree $-1$.

>>>>

A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$, see Definition \ref{dfn: fnl} in the appendix. 
The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
\begin{equation}\label{bvcplx}
\left(\cO(\cE), Q + \{I,-\}\right) .
\end{equation}
In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
We will refer to this as the {\bf classical BV complex} of the theory.

@@

Let $(E, Q, \omega, I)$ be a classical BV theory. 
%and suppose $\psi_0 \in \sE$ is a fixed solution to the equations of motion. 
We recall the formalism of \cite{CG1,CG2} which extracts a factorization algebra on spacetime.

@@

Notice that the BV complex we defined in the previous section, Equation (\ref{bvplx}), is the global sections of the factorization algebra along $M$.
The BV complex can be thought of as the complex of functions on the derived critical locus of the action functional.
It makes sense to restrict fields to any open set $U \subset M$. 
Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the action functional where we restrict the theory to $U$.

The fact that the assignment $U \mapsto \Obs(U)$ defines a factorization algebra can be found in Proposition ?? of \cite{CG2}.

@@

If $M$ is a smooth manifold, its {\em de Rham stack}, as a dg ringed space, is 
\[
M_{\rm dR} = \left(M , (\Omega^\bu_M, \d_{\rm dR})\right) .
\]

If $X$ is a complex manifold, there are two naturally associated dg ringed spaces that will be important for us. 
The first is the $\dbar$-{\em stack}, defined by
\[
X_{\dbar} = \left(M , (\Omega^{0,\bu}_X, \dbar) \right) .
\]
The next is the {\em Dolbeault stack}, defined by
\[
X_{\rm Dol} = \left(M, (\Omega^{\bu,\bu}_X, \dbar)\right) .
\] 
Note that as sheaves of dg modules, there is a quasi-isomorphism $(\Omega^{p,*}_M, \dbar) = \Omega^{p, hol}_M$.
Thus, one can think of the underlying ring of the Dolbeault stack as functions on the shifted holomorphic tangent bundle $T^{1,0} [1] M$ of $M$.

@@

\begin{dfn}
Let $X,Y$ be complex manifolds and $M$ a smooth manifold.
Let $\fg$ be an $L_\infty$ algebra which is finite dimensional in each cohomological degree. 
The {\bf mixed holomorphic-Dolbeault-topological BRST theory} \brian{blah, terrible name} on $X \times Y \times M$ is the local $L_\infty$ algebra defined by
\[
\cF[-1] = \Omega^{0,\bu}_X \Hat{\otimes} \Omega^{\bu,\bu}_Y \Hat{\otimes} \Omega^\bu_M \otimes \fg .
\] 
The $L_\infty$ structure is the one induced from $\fg$ together with the dg commutative product on differential forms. 
This is a classical BRST theory by choosing $Q_{BRST} = 0$ and $I_{BRST} = 0$. 
In other words, $\cF$ is defined by the mapping stack
\[
{\rm Map} (X_{\dbar} \times Y_{\rm Dol} \times M_{\rm dR}, B \fg) .
\]

The {\bf mixed holomorphic-Dolbeault-topological BF theory} is the BV theory given by the $(-1)$-shifted cotangent bundle to $\cF$.
\end{dfn}

Unpacking the definition \brian{unpack and write out action explicitly?}

@@

Fix a Calabi-Yau manifold $X$ of {\em complex} dimension $n$, a smooth manifold of {\em real} dimension $m$, and let $\fg$ be a $\ZZ/2$-graded Lie algebra with a non-degenerate graded symmetric pairing of parity opposite to $n+m$. 
In particular, if $n+m$ is odd, we can take an ordinary complex semi-simple Lie algebra $\fg$ with its Killing form. 
When $n+m$ is even, we must work with a graded Lie algebra with an odd pairing.
In any case, we denote the pairing on $\fg$ by $\<-,-\>$.

\begin{dfn}
Let $X, M$, and $\fg$ be as above.
{\bf Mixed Chern-Simons theory} on $X \times M$ with values in $\fg$ is the $\ZZ/2$-graded classical field theory $(E_\mCS, Q_\mCS, \omega_\mCS, I_\mCS)$, where the space of fields is given by
\[
\cE_\mCS = \Omega^{0,\bullet}(X) \Hat{\otimes} \Omega^\bu(M) \otimes \fg [1] .
\]
The linear part of the BV differential is
\[
Q_{\mCS} = \dbar \otimes 1 \otimes 1 + 1 \otimes \otimes 1 \otimes \d_{\dR}
\]
where $\dbar$ is the Dolbeault differential on $X$, and $\d_{\dR}$ is the de Rham differential on $M$.
The pairing $\omega_\hCS$ is
\[
\omega_{\hCS} (\alpha,\beta) = \<\alpha \wedge \beta\> \wedge \Omega_X ,
\]
where $\Omega_X$ is the Calabi-Yau structure on $X$.
Finally, the interaction $I_\hCS$ is
\[
I_{\hCS}(\alpha) = \frac 16 \<\alpha \wedge [\alpha, \alpha]\> \wedge \Omega_X .
\]
As a mapping stack, mixed Chern-Simons is given by
\[
{\rm Map} (X_{\dbar} \times M_{\dR} , B \fg) .
\]

By convention, when $X$ is the trivial complex manifold we take $\Omega_X = 1$.

\begin{eg}
The most basic  example is to take $X$ trivial and $\dim_{\RR} (M) = 3$.
Then we obtain ordinary Chern-Simons theory on $M$. 
Of course, this theory admits an obvious lift to a $\ZZ$-graded BV theory. 
\end{eg}

\begin{eg} 
Now, take $M$ to be trivial and let $X$ be a Calabi-Yau $2$-fold, like $\CC^2$.
Since $n + m = 2$ is even, we must take a graded Lie algebra with odd pairing. 
First, let $\fh$ be an ordinary Lie algebra equipped with an invariant non-degenerate symmetric pairing $\<-,-\>_\fh$. 
Define the $\ZZ/2$-graded Lie algebra
\[
\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3] 
\]
where $\epsilon_i$ are odd formal variables.

@@

With this data, holomorphic Chern-Simons on the $2$-fold $X$ with values in $\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3]$ is defined. In fact, in this example, there is a natural lift to a $\ZZ$-graded theory whereby the coordinates $\epsilon_i$ are given cohomological degree $-1$.
